Self Regulation Ontology Retest Analyses

### 2018-08-06 code/SRO_Retest_Analyses.Rmd
changed task group labels to title lettering

#Manual correction
tmp = tmp %>%
  mutate(task = ifelse(task_group == 'holt laury survey', "task", as.character(task))) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk task",task_group))) %>%
  mutate(task_group = gsub("survey", "", task_group))
```

@@

>>>>

#Manual correction
tmp = tmp %>%
  mutate(task = ifelse(task_group == 'holt laury survey', "task", as.character(task))) %>%
  mutate(task_group = ifelse(task_group == "psychological refractory period two choices", "psychological refractory period", ifelse(task_group == "angling risk task always sunny", "angling risk", ifelse(task_group == "two stage task", "two step", ifelse(task_group == "threebytwo", "task switching", ifelse(task_group == "adaptive n back", "adaptive n-back", ifelse(task_group == "go nogo", "go/no-go",  ifelse(task_group == "ravens", "raven's", task_group)))))))) %>%
  mutate(task_group = gsub("survey", "", task_group),
         task_group = gsub("task", "", task_group),
         task_group = str_to_title(task_group))
```

```{r}
trial_num_info = tmp %>%
  group_by(task_group) %>%
  summarise(mean_num_all_trials = round(mean(num_all_trials)),
            num_measures = length(unique(dv)))

tmp = tmp %>%
  left_join(trial_num_info, by="task_group")
```

@@

Task level summary of bootstrapped reliabilities.
